---
title: "Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The raw data are cleaned by filling missing dates with `NA` values. This ensures that all locations share the same grid of dates and no single day is skipped. Then, `NA` values are replaced with the previous non-`NA` value or `0`.

The data are available at different levels of granularity: admin area level 1 (administrative area of top level, usually countries), admin area level 2 (usually states, regions, cantons), admin area level 3 (usually cities, municipalities).


| Variable                              | Description                                                  |
| ----------------------------------------------- | ----------------------------------------------------------- |
| `id`                                  | Unique identifier.                                         |
| `date`                                | Observation date.                                            |
| `deaths`                              | Cumulative number of  deaths.                                |
| `confirmed`                           | Cumulative number of  confirmed cases.                       |
| `tests`                               | Cumulative number of  tests.                                 |
| `recovered`                           | Cumulative number of patients released from hospitals or reported recovered. |
| `hosp`                                | Number of hospitalized patients on date.                     |
| `icu`                                 | Number of hospitalized patients in ICUs on date.             |
| `vent`                                | Number of patients requiring invasive ventilation on date.   |
| `population`                                 | Total population.                                            |
| `school_closing`                      | 0: No measures - 1: Recommend closing - 2: Require closing (only some levels or categories, eg just high school, or just public schools - 3: Require closing all levels. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `workplace_closing`                   | 0: No measures - 1: Recommend closing (or work from home) - 2: require closing for some sectors or categories of workers - 3: require closing (or work from home) all-but-essential workplaces (eg grocery stores, doctors). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `cancel_events`                       | 0: No measures - 1: Recommend cancelling - 2: Require cancelling. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `gatherings_restrictions`             | 0: No restrictions - 1: Restrictions on very large gatherings (the limit is above 1000 people) - 2: Restrictions on gatherings between 100-1000 people - 3: Restrictions on gatherings between 10-100 people - 4: Restrictions on gatherings of less than 10 people. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `transport_closing`                   | 0: No measures - 1: Recommend closing (or significantly reduce volume/route/means of transport available) - 2: Require closing (or prohibit most citizens from using it). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `stay_home_restrictions`              | 0: No measures - 1: recommend not leaving house - 2: require not leaving house with exceptions for daily exercise, grocery shopping, and "essential" trips - 3: Require not leaving house with minimal exceptions (e.g. allowed to leave only once every few days, or only one person can leave at a time, etc.). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `internal_movement_restrictions`      | 0: No measures - 1: Recommend closing (or significantly reduce volume/route/means of transport) - 2: Require closing (or prohibit most people from using it). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `international_movement_restrictions` | 0: No measures - 1: Screening - 2: Quarantine arrivals from high-risk regions - 3: Ban on high-risk regions - 4: Total border closure. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `information_campaigns`               | 0: No COVID-19 public information campaign - 1: public officials urging caution about COVID-19 - 2: coordinated public information campaign (e.g. across traditional and social media). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `testing_policy`                      | 0: No testing policy - 1: Only those who both (a) have symptoms AND (b) meet specific criteria (eg key workers, admitted to hospital, came into contact with a known case, returned from overseas) - 2: testing of anyone showing COVID-19 symptoms - 3: open public testing (eg  "drive through" testing available to asymptomatic people). [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `contact_tracing`                     | 0: No contact tracing - 1: Limited contact tracing, not done for all cases - 2: Comprehensive contact tracing, done for all cases. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `stringency_index`                    | Stringency of governmental responses. [More details](https://www.bsg.ox.ac.uk/sites/default/files/2020-04/BSG-WP-2020-032-v5.0.pdf) |
| `administrative_area_level`                             | Administrative area level.                            |
| `administrative_area_level_1`                             | Administrative area of top level.                            |
| `administrative_area_level_2`                               | Administrative area of a lower level, usually states, regions or cantons. |
| `administrative_area_level_3`                                | Administrative are of a lower level, usually cities or municipalities. |
| `latitude`                                 | Latitude.                                                    |
| `longitude`                                 | Longitude.                                                   |


## Latest Data

| URL                              | Description                                                  | Granularity | Format |
| ----------------------------------------------- | ----------------------- | --------------------------- | --- |
| https://storage.covid19datahub.io/data-1.csv | Clean data | Administrative area level 1 | CSV |
| https://storage.covid19datahub.io/data-2.csv | Clean data | Administrative area level 2 | CSV |
| https://storage.covid19datahub.io/data-3.csv | Clean data | Administrative area level 3 | CSV |
| https://storage.covid19datahub.io/data-1.zip | Clean data | Administrative area level 1 | ZIP |
| https://storage.covid19datahub.io/data-2.zip | Clean data | Administrative area level 2 | ZIP |
| https://storage.covid19datahub.io/data-3.zip | Clean data | Administrative area level 3 | ZIP |
| https://storage.covid19datahub.io/rawdata-1.csv | Raw data | Administrative area level 1 | CSV |
| https://storage.covid19datahub.io/rawdata-2.csv | Raw data | Administrative area level 2 | CSV |
| https://storage.covid19datahub.io/rawdata-3.csv | Raw data | Administrative area level 3 | CSV |
| https://storage.covid19datahub.io/rawdata-1.zip | Raw data | Administrative area level 1 | ZIP |
| https://storage.covid19datahub.io/rawdata-2.zip | Raw data | Administrative area level 2 | ZIP |
| https://storage.covid19datahub.io/rawdata-3.zip | Raw data | Administrative area level 3 | ZIP |
| https://storage.covid19datahub.io/data.log | Clean data - Log file | All levels | CSV |
| https://storage.covid19datahub.io/rawdata.log | Raw data - Log file | All levels | CSV |
| https://storage.covid19datahub.io/src.csv | Data sources | All levels | CSV |


## Vintage Data

```{r, include=FALSE}
start <- as.Date("2020-04-14")
end   <- Sys.Date()-2
dates <- seq(end, start, by = -1)
tab   <- sprintf("| https://storage.covid19datahub.io/%s.zip | Dataset snapshot (vintage) | %s | ZIP |", dates, dates)
tab   <- paste0(tab, collapse = "\n")
```


| URL                              | Description                                                  | Date | Format |
| ----------------------------------------------- | --------------------------- | ----------------------- | --- |
`r tab`

`r readr::read_file('terms.md')`
